Differential Expression

### 2020-03-27 cmc-rnaseq-de/Differential-Expression.Rmd
error with inputs

### Data download
#### Obtain filtered and CQN normalized counts
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
# Download CQN counts
CQN_ID = "syn21825509"
ALL_USED_IDs = c(ALL_USED_IDs, CQN_ID)
CQN.GENE_EXPRESSION$E = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id")

@@

# Fit linear model using new weights and new design
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION,
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

@@

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION$E)

>>>>

### Data download
#### Obtain filtered and CQN normalized counts
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}

# Download CQN counts
CQN_ID = "syn21825509"
ALL_USED_IDs = c(CQN_ID)
CQN.GENE_EXPRESSION = downloadFile(CQN_ID) %>% 
  tibble::column_to_rownames(var = "ensembl_gene_id")

@@

# Fit linear model using new weights and new design
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION,
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

@@

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION)
